### 2021-05-17 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
Place all tikz pictures in imgs\ directory
Remove some un-needed comments
Apply minor changes to some .tex files

In order to not consider individuals that will be lost to the system, the set of 
accepting states needs to be taken into consideration. 
As defined in section \ref{sec:waiting-time}, the set of accepting states is 
given by \ref{eq:accepting-states-class-2}:

@@

% For the waiting time formula in sections \ref{sec:recursive-waiting-time-others}
% and \ref{sec:recursive-waiting-time-ambulance}
% the mean sojourn time for each state was considered,
% ignoring any arrivals.
% Here, the same approach is used but ignoring only class 2
% arrivals. That is because for the waiting time formula, once an individual enters 
% the service centre (i.e. starts waiting) any individual arriving after them will 
% not affect their
% pathway. That is not the case for blocking time. When a class 2 individual is 
% blocked, 
% any class 1 individual that arrives will cause the blocked individual to remain 
% blocked for more time. Therefore, class 1 arrivals are considered here:

@@

To illustrate how the described formula works consider a Markov model where 
\(C=2, T=2, N=4, M=2\) (figure \ref{fig:example-algeb-blocking}). 
The equations that correspond to such a model are shown in 
(\ref{eq:first_eq_of_blocking_example})-(\ref{eq:last_eq_of_blocking_example}) 
and their equivalent matrix notation form is shown in 
\ref{eq:example_algebaric_approach_blocking_time}.

\begin{minipage}{.5\textwidth}
    \begin{figure}[H]
        \scalebox{0.6}{\input{sections/queueing_model/subsections/example/example_2242/main.tex}}
        \caption{
            \centering{Example of Markov chain with \(C=2, T=2, N=4, M=2\)}
        }
        \label{fig:example-algeb-blocking}
    \end{figure}
\end{minipage}
\begin{minipage}{.43\textwidth}
    \begin{align}
        b(1,2) &= c(1,2) + p_o b(1,3) \label{eq:first_eq_of_blocking_example} \\
        b(1,3) &= c(1,3) + p_s b(1,2) \nonumber \\ &+ p_o b(1,4) \\
        b(1,4) &= c(1,4) + b(1,3) \\
        b(2,2) &= c(2,2) + p_s b(1,2) \nonumber \\ &+ p_o b(2,3) \\
        b(2,3) &= c(2,3) + p_s b(2,2) \nonumber \\ &+ p_o b(1,4) \\
        b(2,4) &= c(2,4) + b(2,3) \label{eq:last_eq_of_blocking_example}
    \end{align}
\end{minipage}

>>>>

In order to not consider individuals that will be lost to the system, the set of 
accepting states needs to be taken into consideration. 
As defined in section \ref{sec:waiting_time}, the set of accepting states is 
given by \ref{eq:accepting_states_class_2}:

@@

@@

To illustrate how the described formula works consider a Markov model where 
\(C=2, T=2, N=4, M=2\) (figure \ref{fig:example_algeb_blocking}). 
The equations that correspond to such a model are shown in 
(\ref{eq:first_eq_of_blocking_example})-(\ref{eq:last_eq_of_blocking_example}) 
and their equivalent matrix notation form is shown in 
\ref{eq:example_algebaric_approach_blocking_time}.

\begin{minipage}{.5\textwidth}
    \begin{figure}[H]
        \scalebox{0.6}{\input{imgs/example_2242/main.tex}}
        \caption{
            \centering{Example of Markov chain with \(C=2, T=2, N=4, M=2\)}
        }
        \label{fig:example_algeb_blocking}
    \end{figure}
\end{minipage}
\begin{minipage}{.43\textwidth}
    \begin{align}
        b(1,2) &= c(1,2) + p_o b(1,3) \label{eq:first_eq_of_blocking_example} \\
        b(1,3) &= c(1,3) + p_s b(1,2) \nonumber \\ &+ p_o b(1,4) \\
        b(1,4) &= c(1,4) + b(1,3) \\
        b(2,2) &= c(2,2) + p_s b(1,2) \nonumber \\ &+ p_o b(2,3) \\
        b(2,3) &= c(2,3) + p_s b(2,2) \nonumber \\ &+ p_o b(1,4) \\
        b(2,4) &= c(2,4) + b(2,3) \label{eq:last_eq_of_blocking_example}
    \end{align}
\end{minipage}

### 2021-05-17 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Apply minor changes to some .tex files

\subsubsection{Waiting time}
% TODO: Include recursive formula as well??

@@

\begin{equation}\label{eq:accepting-states-class-1}
    S_A^{(1)} = \{(u, v) \in S \; | \; v < N \}
\end{equation}

@@

\begin{equation}\label{eq:accepting-states-class-2}
    S_A^{(2)}=
    \begin{cases}
        \{(u, v) \in S \; | \; u < M \}, & \textbf{if } T \leq N\\
        \{(u, v) \in S \; | \; v < N \}, & \textbf{otherwise}
    \end{cases}
\end{equation}

Note here that if the threshold is less than or equal the total capacity of the
system the set includes all states that are not on the last column of the 
Markov chain.
Otherwise, the set of accepting state is identical to 
\ref{eq:accepting-states-class-1}. Thus, the expressions for the waiting times 
for class 1 and class 2 individuals are given by:

\begin{equation} \label{eq:closed_form_waiting_others}
    W^{(1)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(1)} \\ v \geq C}} 
    \frac{1}{C \mu} \times (v-C+1) \times \pi(u,v)}{\sum_{(u,v) \, 
    \in S_A^{(1)}} \pi(u,v)}
\end{equation}

\begin{equation}\label{eq:closed_form_waiting_ambulance}
    W^{(2)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(2)} \\ min(v,T) \geq C}} 
    \frac{1}{C \mu} \times (\min(v+1,T)-C) \times \pi(u,v)}{\sum_{(u,v) \, 
    \in S_A^{(2)}} \pi(u,v)}
\end{equation}

@@

The two coefficients represent the proportion of individuals of each type that 
did not get lost and traversed through the model.
Thus, one should account for the probability that an individual is lost to the 
system. 
This probability can be easily calculated by using the two sets of accepting 
states \(S_A^{(2)}\) and \(S_A^{(1)}\) defined in equations 
\ref{eq:accepting-states-class-1} and \ref{eq:accepting-states-class-2}. 
Using these equations the probability, for either class type, that an individual 
is not lost in the system is given by:

@@

\begin{equation}\label{overall_waiting_time}
    W = \frac{\lambda_1 P(L'_1)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(1)} + 
    \frac{\lambda_2 P(L'_2)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(2)}
\end{equation}

>>>>

\subsubsection{Waiting time} \label{sec:waiting_time}

@@

\begin{equation}\label{eq:accepting_states_class_1}
    S_A^{(1)} = \{(u, v) \in S \; | \; v < N \}
\end{equation}

@@

\begin{equation}\label{eq:accepting_states_class_2}
    S_A^{(2)}=
    \begin{cases}
        \{(u, v) \in S \; | \; u < M \}, & \textbf{if } T \leq N\\
        \{(u, v) \in S \; | \; v < N \}, & \textbf{otherwise}
    \end{cases}
\end{equation}

Note here that if the threshold is less than or equal the total capacity of the
system the set includes all states that are not on the last column of the 
Markov chain.
Otherwise, the set of accepting state is identical to 
\ref{eq:accepting_states_class_1}. Thus, the expressions for the waiting times 
for class 1 and class 2 individuals are given by:

\begin{equation} \label{eq:closed_form_waiting_class_1}
    W^{(1)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(1)} \\ v \geq C}} 
    \frac{1}{C \mu} \times (v-C+1) \times \pi(u,v)}{\sum_{(u,v) \, 
    \in S_A^{(1)}} \pi(u,v)}
\end{equation}

\begin{equation}\label{eq:closed_form_waiting_class_2}
    W^{(2)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(2)} \\ min(v,T) \geq C}} 
    \frac{1}{C \mu} \times (\min(v+1,T)-C) \times \pi(u,v)}{\sum_{(u,v) \, 
    \in S_A^{(2)}} \pi(u,v)}
\end{equation}

@@

The two coefficients represent the proportion of individuals of each type that 
did not get lost and traversed through the model.
Thus, one should account for the probability that an individual is lost to the 
system. 
This probability can be easily calculated by using the two sets of accepting 
states \(S_A^{(2)}\) and \(S_A^{(1)}\) defined in equations 
\ref{eq:accepting_states_class_1} and \ref{eq:accepting_states_class_2}. 
Using these equations the probability, for either class type, that an individual 
is not lost in the system is given by:

@@

\begin{equation}\label{eq:overall_waiting_time}
    W = \frac{\lambda_1 P(L'_1)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(1)} + 
    \frac{\lambda_2 P(L'_2)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(2)}
\end{equation}
